---
output:
  md_document:
    variant: markdown_github
---

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/BFS)](https://CRAN.R-project.org/package=BFS)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## BFS

```{r options, echo=FALSE}
knitr::opts_chunk$set(cache = FALSE, 
                      warning = FALSE, 
                      error = FALSE, 
                      eval = TRUE,
                      fig.path = "")

library(BFS)
```

### Introduction

The `BFS` package allows the user to download public data from the 
[Swiss Federal Statistical Office (BFS)](https://www.bfs.admin.ch/bfs/en/home.html){target="_blank"}
in a dynamic and reproducible way.

The package can be installed from Github (development version):

```{r install, eval=FALSE}
# From Github
library(devtools)
install_github("lgnbhl/BFS")
library(BFS)
```

### Usage Example

The `bfs_get_metadata` function returns a data frame/tibble containing the titles, 
publication dates, observation periods, website urls and download urls of available 
BFS datasets in a given language (in German by default):

```{r bfs_get_metadata, eval=FALSE}
meta_de <- bfs_get_metadata()
```

You can also retrieve the metadata in French ("fr"), Italian ("it") or English ("en").
Note that Italian and English languages give access to less datasets.

To find a dataset, use either `View` in Rstudio or `bfs_search`:

```{r bfs_search, eval=FALSE}
meta_en <- bfs_get_metadata(language = "en")
meta_en_edu <- bfs_search("education", data = df_en)
```

To download the BFS dataset, select the `url_px` link from the metadata.

```{r bfs_get_dataset, eval=FALSE}
df_edu <- bfs_get_dataset(meta_en_edu$url_px[3])
df_edu
```

### Other information

This package is in no way officially related to or endorsed by the Swiss Federal Statistical Office (BFS).
